Kindly Bent to Free Us

### 2019-02-20 kindly/soa.tex
vault

\section{Related works}

@@

Alms~\citep{DBLP:conf/popl/TovP11},
F$^\circ$~\citep{DBLP:conf/tldi/MazurakZZ10},
Quill~\citep{DBLP:conf/icfp/Morris16},
Linear Haskell~\citep{DBLP:journals/pacmpl/BernardyBNJS18}

>>>>

\section{Related work}

@@

Alms~\citep{DBLP:conf/popl/TovP11},
F\degree~\citep{DBLP:conf/tldi/MazurakZZ10},
Quill~\citep{DBLP:conf/icfp/Morris16},
Linear Haskell~\citep{DBLP:journals/pacmpl/BernardyBNJS18},
Vault\citep{DBLP:conf/pldi/DeLineF01,DBLP:conf/pldi/FahndrichD02}
